The Poisson approximate likelihood compared to the particle filter

### 2024-07-22 ms.Rnw
set seeds

bake(file = "output/round_01/ovov_01_el.rds",{
  el_01 <- measlespkg::eval_logLik(mifs_global_01, ncores=ncores, np_pf = NP_MIF, nreps=ncores)
  el_01
})
@

@@

bake(file = "output/round_02/ovov_mif_02.rds",{ 
  mifs_global_02 <- foreach(i=1:ncores,.packages='pomp', .options.multicore=mcopts) %dopar% {
  panelPomp::mif2(
    sir_panel,
    Np = NP_MIF,
    cooling.fraction.50 = 0.5,
    rw.sd = rw_sd(beta1=0.01*sd_02,beta2=0.01*sd_02,beta3=0.01*sd_02,
                  beta11=0.01*sd_02,phi=0.01*sd_02,sigma_q=0.01*sd_02,sigma_xi=0.01*sd_02,
                  S10=ivp(0.24)*sd_02,I10=ivp(0.24)*sd_02,R10=ivp(0.24)*sd_02,
                  S20=ivp(0.24)*sd_02,I20=ivp(0.24)*sd_02,R20=ivp(0.24)*sd_02,
                  S30=ivp(0.24)*sd_02,I30=ivp(0.24)*sd_02,R30=ivp(0.24)*sd_02),
    cooling.type = "geometric",
    Nmif = NMIF,
    shared.start = numeric(0),
    specific.start = starting_values_02[[i]],
    block = F
  ) 
}
  mifs_global_02
})

bake(file = "output/round_02/ovov_02_el.rds",{
  el_02 <- measlespkg::eval_logLik(mifs_global_02, ncores = ncores, np_pf = NP_MIF, nreps=ncores)
  el_02
})
@

@@

bake(file = "output/round_03/ovov_mif_03.rds",{ 
  mifs_global_03 <- foreach(i=1:ncores,.packages='pomp', .options.multicore=mcopts) %dopar% {
  panelPomp::mif2(
    sir_panel,
    Np = NP_MIF,
    cooling.fraction.50 = 0.5,
    rw.sd = rw_sd(beta1=0.01*sd_03,beta2=0.01*sd_03,beta3=0.01*sd_03,
                  beta11=0.01*sd_03,phi=0.01*sd_03,sigma_q=0.01*sd_03,sigma_xi=0.01*sd_03,
                  S10=ivp(0.24)*sd_03,I10=ivp(0.24)*sd_03,R10=ivp(0.24)*sd_03,
                  S20=ivp(0.24)*sd_03,I20=ivp(0.24)*sd_03,R20=ivp(0.24)*sd_03,
                  S30=ivp(0.24)*sd_03,I30=ivp(0.24)*sd_03,R30=ivp(0.24)*sd_03),
    cooling.type = "geometric",
    Nmif = NMIF,
    shared.start = numeric(0),
    specific.start = starting_values_03[[i]],
    block = F
  ) 
}
  mifs_global_03
})

bake(file = "output/round_03/ovov_03_el.rds",{
  el_03 <- measlespkg::eval_logLik(mifs_global_03, ncores = ncores, np_pf = NP_MIF, nreps=ncores)
  el_03
})
@

>>>>

bake(file = "output/round_01/ovov_01_el.rds",{
  set.seed(33124)
  el_01 <- measlespkg::eval_logLik(mifs_global_01, ncores=ncores, np_pf = NP_MIF, nreps=ncores)
  el_01
})
@

@@

bake(file = "output/round_02/ovov_mif_02.rds",{ 
  mifs_global_02 <- foreach(i=1:ncores,.packages='pomp', .options.multicore=mcopts) %dopar% {
    set.seed(202407222+1234*i)
    panelPomp::mif2(
      sir_panel,
      Np = NP_MIF,
      cooling.fraction.50 = 0.5,
      rw.sd = rw_sd(beta1=0.01*sd_02,beta2=0.01*sd_02,beta3=0.01*sd_02,
                    beta11=0.01*sd_02,phi=0.01*sd_02,sigma_q=0.01*sd_02,sigma_xi=0.01*sd_02,
                    S10=ivp(0.24)*sd_02,I10=ivp(0.24)*sd_02,R10=ivp(0.24)*sd_02,
                    S20=ivp(0.24)*sd_02,I20=ivp(0.24)*sd_02,R20=ivp(0.24)*sd_02,
                    S30=ivp(0.24)*sd_02,I30=ivp(0.24)*sd_02,R30=ivp(0.24)*sd_02),
      cooling.type = "geometric",
      Nmif = NMIF,
      shared.start = numeric(0),
      specific.start = starting_values_02[[i]],
      block = F
    ) 
  }
  mifs_global_02
})

bake(file = "output/round_02/ovov_02_el.rds",{
  set.seed(4321)
  el_02 <- measlespkg::eval_logLik(mifs_global_02, ncores = ncores, np_pf = NP_MIF, nreps=ncores)
  el_02
})
@

@@

bake(file = "output/round_03/ovov_mif_03.rds",{ 
  mifs_global_03 <- foreach(i=1:ncores,.packages='pomp', .options.multicore=mcopts) %dopar% {
    set.seed(2207+4321*i)
    panelPomp::mif2(
      sir_panel,
      Np = NP_MIF,
      cooling.fraction.50 = 0.5,
      rw.sd = rw_sd(beta1=0.01*sd_03,beta2=0.01*sd_03,beta3=0.01*sd_03,
                    beta11=0.01*sd_03,phi=0.01*sd_03,sigma_q=0.01*sd_03,sigma_xi=0.01*sd_03,
                    S10=ivp(0.24)*sd_03,I10=ivp(0.24)*sd_03,R10=ivp(0.24)*sd_03,
                    S20=ivp(0.24)*sd_03,I20=ivp(0.24)*sd_03,R20=ivp(0.24)*sd_03,
                    S30=ivp(0.24)*sd_03,I30=ivp(0.24)*sd_03,R30=ivp(0.24)*sd_03),
      cooling.type = "geometric",
      Nmif = NMIF,
      shared.start = numeric(0),
      specific.start = starting_values_03[[i]],
      block = F
    ) 
  }
  mifs_global_03
})

bake(file = "output/round_03/ovov_03_el.rds",{
  set.seed(1234)
  el_03 <- measlespkg::eval_logLik(mifs_global_03, ncores = ncores, np_pf = NP_MIF, nreps=ncores)
  el_03
})
@
